Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-09 paper/paper.tex
few more edits

\section{Mined JS Files}
\label{sec:seeds}
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files from the suites
of public engines, and 4) test files mined from issue trackers of
these engines.

@@

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed \testsThatFail{}
test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc and
\testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
shows the number of test cases whose executions do not throw
dynamic type errors in any of the engines because of an undefined variable or property.
These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. For the evaluation of test transplantation, we used
the \totalTestFilesForTestTransplantation{} tests included in the
dashed rectangle under column ``type-in-all'', \ie{}, all tests under
that column but the Test262 tests. We did not consider tests from the
conformance suite as they are more likely to indicate missing features
as opposed to bugs. In addition, engine developers have access to
these test and are encouraged to run them. Finally, column
``no-fail-in-all'' shows the tests for which all engines pass. Note
that the set of tests in this column is a subset of the
``type-in-all'' test set. This test set is used in the evaluation of
differential testing as fuzzing seeds. The guarantee that they pass in
all engines assures that, if discrepancies occur, they are related to
the changes in the input as opposed to the original cause of failure.

@@

\subsection{Mining Tests from Issue Trackers}

>>>>

\section{Mined JS Files}
\label{sec:seeds}
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files from the suites
of public engines (ie., Duktape, JerryScript, JSI, and Tiny-js),
4) test files mined from issue trackers of
these engines, and 5) test files from other GitHub projects.

@@

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed \testsThatFail{}
test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc and
\testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
shows the number of test cases whose executions do not throw
dynamic type errors in any of the engines because of an undefined variable or property.
These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. \Fix{Similarly, the \chakra project does not use the default
well-known assertions available in JS, which the other JS engines use.
Instead, it uses its own testing framework, WScript. In this case, we could
not easily reproduce the \chakra unit tests in the other engines since it would
raise a ReferenceError. Also, updating the other engines to use WScript would
require a non-trivial manual process.}

For the evaluation of test transplantation, we used
the \totalTestFilesForTestTransplantation{} tests included in the
dashed rectangle under column ``type-in-all'', \ie{}, all tests under
that column but the Test262 tests. We did not consider tests from the
conformance suite as they are more likely to indicate missing features
as opposed to bugs. In addition, engine developers have access to
these test and are encouraged to run them. Finally, column
``no-fail-in-all'' shows the tests for which all engines pass. Note
that the set of tests in this column is a subset of the
``type-in-all'' test set. This test set is used in the evaluation of
differential testing as fuzzing seeds. The guarantee that they pass in
all engines assures that, if discrepancies occur, they are related to
the changes in the input as opposed to the original cause of failure.

@@

\subsection{Mining Tests}

\subsubsection{from GitHub projects}

\Fix{We mined JS programs from the GitHub repository. In this case, we searched
for projects written in JavaScript, that were tagged with ``javascript-engine",
and that have both ``Javascript" and ``engine" the name or the description of
the project. After this process, we ended up with 2200 JS programs, which we
downloaded locally. However, after careful investigation, we noted that 160 of
these projects do not  have any JS file, which were excluded from our study.
We used the 2040 remaining ones as input to our testing approaches.}

\subsubsection{from Issue Trackers}
